\chapter{Discussion}
In this chapter, individual case-by-case study will be discussed in detail. The results from our measurements will also be compared with the counterparts form Weder et al.

\section {Participant 3}
The results from this participant was the closest one to the results reported by Weder et al. For the oxygenated hemoglobin HbO waveform morphology, tonic response could be observed in channel 1, 2, and 3, and phasic response could be observed in channel 10 and 12.

\section {Participant 5}
For the oxygenated hemoglobin HbO waveform, there were significantly larger on-sets for the 90 dB sound stimuli in Channel 1, 2, and 3, i.e. around the Broca's area.

Apart from this, the waveforms for deoxygenated hemoglobin, HbR, were also quite different from the ones Weder et al. reported. For the loudest sound stimuli, channels overlying the caudal superior temporal gyrus and channels over Broca's area showed clear phasic response. 

\section {Participant 6}

For the oxygenated hemoglobin, HbO waveform, the loudest sound stimuli resulted in phasic response for almost all the channels. In addition, it also resulted in faster on-set compared with other stimuli of lower sound pressure levels.

On the other hand, as for the deoxygenated hemoglobin, HbR response, results from multiple channels appeared to be noisy even if the SCI values were already above the suggested threshold.


\section {Participant 7}

The results from this participant are rather indeterminant to differentiate between response to different sound pressure levels.


\section {Participant 8}
This participant was given only silence stimuli. No pattern could be concluded for the measured waveform morphology. Nonetheless, it's noteworthy to know that even if there are almost no visual and sound stimuli, dynamic hemoglobin response still exists.

\section {Regional Analysis}
In comparison to the research from Weder et al, we chose a different approach to define our region of interest. Instead of first looking at the results and grouping different regions according to similar waveforms. We are interested to know how the responses from the auditory cortex would be compared with other regions of the measured left brain hemisphere.

The auditory cortex was the main interest of this study. It is around the caudal superior temporal gyrus. We compared the hemoglobin response from the three channels over the auditory cortex with all the other channels lying on the rest of the measured left brain hemisphere. The waveform morphology of the auditory cortex is very similiar to the counterparts of the rest of the measured parts. In other words, the dynamic hemoglobin response of the auditory cortex represents that of the entire left brain hemisphere fairly well.